Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping

### 2018-01-30 stp/paper_aaai/main.tex
shortened to 6 pages

In our case, we would like this global model to account not only for structural properties of the original data sources, but also to include the semantics, which is usually implicitly present in the sources.
In other words, we want to build a semantic model which describes the data sources in terms of concepts and relationships defined by an ontology \cite{taheriyan2016learning}.
Henceforth, we focus on a specific data integration problem: automatically mapping a new relational data source onto a user provided ontology.
}
Relational data sources are still one of the most popular ways to store enterprise or Web data. However, the issue with relational schema is the lack of a well-defined semantic description.
A common ontology provides a way of representing the meaning of a relational schema and can facilitate the integration of heterogeneous data sources within a domain.
Indicating semantic correspondences manually might be appropriate if only few data sources need to be integrated, however, it becomes tedious with the growing number of heterogeneous schemata.

@@

%\subsubsection{Example} 
Consider the situation where we have some simple relational database tables with columns $\langle$\textit{Surname, Event, Date}$\rangle$, and 
$\langle$\textit{Company, Festival, Address}$\rangle$.
We do not \textit{a priori} know if ``Date'' is a 
date of birth of the person or the start date of the event (c.f. Fig. \ref{FIG:onto}); or whether 
``Address'' refers to the name of the place where the festival is located, or the 
email address of the company. 
Given an ontology like the one in Fig. \ref{FIG:onto}, we would like to automatically map the new data sources to  the 
ontology.\hfill$\square$

@@

Firstly, we build a graph which includes attributes (i.e. columns) from the new
source as well as ontology classes and properties.
We name it \emph{integration graph}.
It uses information gathered from the previously mapped data sources, and is further extended with information derived from the ontology.
%Firstly, we build a \emph{integration graph} which includes the 
%attributes from the new source as well as ontology classes and properties.
Secondly, we apply machine learning techniques to 
assign costs to its edges. 
Lastly, we use CP to 
find a minimum cost Steiner Tree in the graph.
The goal is to assign the costs on the edges in such a way that the resulting 
Steiner Tree is a valid and coherent semantic model for the new source. 
Our contributions are:
%\begin{itemize}
	%\item 
	A novel modeling framework for the \relonto{} problem that use ML, KRR and CP techniques,
%	\npr{symbolic AI, ontological reasoning, transitive closure}
	%\item
	an efficient approach to handle attributes which cannot be matched to 
	the ontology, \forijcai{arg1, through a new semantic labeling model and a new STP 
	model with additional nodes in the integration graph.}
	%\item 
	a flexible and extensible approach to the problem, which is easy to 
	reuse and adapt to specific situations through the use of CP.\forijcai{ allows introduction of additional constraints with no changes to the solver.} 
%\end{itemize}

@@

\begin{figure}[ht]
\centering
\scalebox{0.8}{
\begin{tikzpicture}
	\node[class] (pe) at (0,0)  {Person};
	\node[class] (co) at (0,-2) {Organisation};
	\node[class] (ev) at (3,0.2) {Event};
	\node[class] (pl) at (5,-1) {Place};
	\node[class] (ci) at (3,-2.5) {City};
	\node[class] (st) at (5,-2.5) {State};

@@

\end{tikzpicture}
}
\caption{Example of ontology
(`\protect\tikz{ \protect\node[class, inner sep = 2] () at (0,0)  {};}' are Classes, `\protect\tikz{ \protect\path[hasaC,->] 
(0,1) -- (3ex,1);}' means ``has an object property'', 
`\protect\tikz{ \protect\path[hasaA,decoration={post length=0}] (0,0) edge[decorate] (3ex,0);}' 
means ``has a data property'' and 
`\protect\tikz{ \protect\path[isa,->] (0,1) -- (3ex,1);}' means ``subClassOf'' ). Example by
\protect\citeasnoun{Taheriyan2013}.
}
\label{FIG:onto}
\vspace{-3mm}
\end{figure}

A \emph{semantic model} $m$ is a directed graph with two types of nodes: 
\emph{class nodes} and \emph{data nodes}. 
We denote them as $\mathcal{C}_m$ and $\mathcal{D}_m$, respectively.
$ \mathcal{C}_m$ corresponds to classes in the ontology 
whereas $\mathcal{D}_m$ corresponds to data 
properties. 
Edges in the semantic model correspond to properties in the ontology, as 
shown in Fig.~\ref{FIG:sem} (notice the same edges appear in Fig.~\ref{FIG:onto}).
The semantic model may have several instances of the same ontology class, that is why class nodes are enumerated.
Semantic models can be formalized using a standard mapping language such as R2RML~\cite{r2rml}.

@@

\subsection{Semantic Labeling}
The semantic types $\mathcal{L_O} = \{l_1, l_2, ..., l_p\}$ of an ontology 
correspond to all pairs $(c,d)$, where $c$ is a Class in $\mathcal{O}$, and $d$ 
is a data property of that class (including inherited properties). 
For example, in Fig. \ref{FIG:onto}, we would get
(City,name) and (State,name).

The first step to model the semantics of a new source $s^\star$ is to recognize the semantic types present in the source. 
We call this step \emph{semantic labeling}, which assigns a confidence value to a match of an attribute from $s^\star$ to a type $l \in 
\mathcal{L_O}$.
Typically semantic labeling techniques encounter several problems such as:
naming conflicts~\cite{Pinkel:rodi}, multiple data representations, and semantically different attributes might have syntactically similar 
content.%, for example, startDate versus endDate for the Event class.
Also, there may be a considerable number of attributes which have no 
corresponding property in the ontology (accidentaly or deliberately).
%\ddg{CHECK!}

We formulate the problem of semantic labeling as a multi-class classification
problem.
The known source descriptions $\Delta_T$ provide us the training sample.
We compute a feature vector for each attribute in a data source and associate 
the known semantic type with the corresponding feature vector.
The feature vector includes, among others, characteristics
such as a number 
of whitespaces and other special characters, statistics of 
values in the column. 
\forijcai{A full list can be found in Appendix \ref{Ann:SemLab}.}
%\npr{If I remove entropy descr, we are perfectly within page limit}
%\ignore{
One of the important features characterising information content of an attribute is Shannon's entropy.
% of the attribute's concatenated rows
Shannon's entropy 
%(or information entropy~\cite{Manning:Introduction})
 of a string $X$ is defined as
$H(X) = -\sum_{i}{p_i \log_{2}p_i},$ where $p_i$ is the probability of a character, whose index in character vocabulary is $i$, to appear in $X$, and the summation ranges over all
characters in the vocabulary.
%of all possible characters
To evaluate $p_i$ in Shannon's entropy, we evaluate normalized character frequency distribution \emph{chardist} of an attribute, as character counts in concatenated rows of the attribute, normalized by the total length of the concatenated rows.
The vocabulary of all characters consists of 100 printable characters (including $\backslash$n).
Finally, we add the 100-dimensional vector of $p_i$ to the attribute feature vector.
%}
We also compute a set of features based on similarity metrics inspired by state-of-the-art works by ~\citeasnoun{Pham:semantic} or~\citeasnoun{Ritze:matching}.
Among others, we compute mean cosine similarity for character distributions of attribute values and string similarity metrics for attribute names.
%To extract features from attribute names, we compute string similarity metrics: minimum edit distance, two WordNet based similarity measures such as JCN~\cite{Jiang:Semantic} and LIN ~\cite{Lin:Information}, and $k$-nearest neighbors using Needle-Wunsch distance~\cite{Needleman:General}.
%The minimum edit distance between two strings $s_1$ and $s_2$ is the minimum number of edit operations, such as insertion, deletion, substitution, which are required to transform one string into another~\cite{Manning:Introduction}.
%We compute the similarity between attribute name and all class instances in the training data.
%The number of thus extracted features depends on the number of semantic labels in the training data.
We train a random forest on the obtained sample.

@@

To provide an integrated view over the known source descriptions $\Delta_T$, we 
align their semantic models as well as all considered semantic 
types. 
This is achieved by constructing an \emph{alignment graph}.

@@

The graph is weighted by a function $w_\mathcal{O} : \mathcal{E_O} \mapsto 
\mathbb{R}$ such that edges which are present in
the known semantic models have lower weights than those 
which are inferred from the ontology.
\forijcai{In the next section we will see that this makes edges from semantic models 
more attractive. }
\citeasnoun{taheriyan2016learning} provide details on the weighting function.
%\ddg{How exactly are they weighted?}
An example alignment graph is illustrated in Fig.~\ref{FIG:ali}. 
%Bigger examples can be found in \cite{Taheriyan2013}. 
Black links are links supported by the known semantic models. 
Blue links are inferred from the ontology.\forijcai{(the orange 
ones correspond to the ones added to connect Classes of the ontology that never 
appeared in the semantic models).}
% and can be assigned the 
%maximum weight $w_max$ \ddg{where does this weight come from?}

\begin{figure}[ht]
\centering \scalebox{0.8}{
\begin{tikzpicture}[scale=0.9]

@@

\end{tikzpicture}}
\caption{Example of alignment graph (`\protect\tikz{ \protect\node[class, inner sep = 2] () at (0,0)  
{};}' \forijcai{`\protect\tikz{ \protect\node[class,orange,fill=orange!30!white,text=black, inner sep = 2] () at 
(0,0)  
{};}'} are class nodes, and `\protect\tikz{ \protect\node[data] () at (0,0)  {};}' are data 
nodes). We omit weights for clarity.}
\label{FIG:ali}
\vspace{-3mm}
\end{figure}

@@

Given a graph $G =
(V, E)$ and a subset of its nodes $T \subseteq V$, a 
Steiner Tree $G_s = (V_s, E_s )$ is a tree (connected acyclic graph) such that 
$T \subseteq V_s \subseteq 
V$ and $E_s \subseteq E$. 
In other words, $G_s$ spans all the nodes in $T$ and 
may include additional nodes from $V$, in particular to ensure the 
connectedness of the constructed tree. 
The Steiner Tree Problem 
(STP) is stated as follows: given $G$ and a weight function $w_f : E 
\mapsto \mathbb{R}$, find the Steiner Tree that minimizes the sum of the 
weights of the edges in $E_s$ given by $w_f$. This was proven to be NP-hard 
by \citeasnoun{Karp1972}.

@@

\begin{figure}[ht]
\centering \scalebox{0.8}{
\begin{tikzpicture}[scale=0.9]
	\node[class, rectangle, rounded corners] (CLASS) at (0,0) { \small{ 
	Class nodes of Alignment Graph (i.e. $\mathcal{C_{G_O}}$)}};

@@

	\path[draw] (a4) -- (stn1);
	\path[draw] (a4) -- (cin1);
	\path[draw] (a4) -- (con1);
	\path[draw] (a4) -- (cin2);
	\path[draw] (a4) -- (con2);
\end{tikzpicture} }
\caption{Example of integration graph. (`\protect\tikz{ \protect\node[att] () at (0,0)  
{};}' are attribute nodes). We omit weights and only show the most likely 
matches for clarity. Data node
are the same as in Fig \ref{FIG:ali}.}
\label{FIG:inte}
\vspace{-3mm}
\end{figure}

@@

\textbf{Patterns:}
As explained in Sec. \ref{SSEC:pattern-mining}, we use 
graph patterns to incentivise the solution tree 
$T^\star$ to contain subgraphs of the alignment graph that have been frequently 
seen in the training set.
To do this, we use the support of each obtained patterns as a prize. If 
the tree contains a pattern, then its weight is automatically reduced by the 
value of the support of that pattern. Sec. \ref{SEC:rel2ontocp} shows how this is integrated in the model.

@@

If an attribute $a$ is matched to $unk_a$, then $unk_a$ will be linked to Class 
node \emph{unknown}. 
The rest of the attributes can then be matched normally 
and build  a semantic model as usual. 
To maintain connectedness of the 
Steiner tree, the \emph{unknown} node and one of the other Class nodes in $T^\star$ 
will 
both be connected to the \emph{root} node. 
Note that if all attributes find a 
match, then both the \emph{unknown} and \emph{root} nodes will not be selected in 
the Steiner tree and the normal behavior will take place.
The weights of the edges between these special nodes are
assigned the same way as for the rest of the edges.
%\ddg{Explain the weights of the edges introduced by the unknown nodes}

@@

A Constraint Optimization Problem (COP) is a tuple $P=(\boldsymbol{v},C,o)$ 
where $\boldsymbol{v}$ is a 
set of \emph{variables}, $C$ is a set of $n$-ary 
\emph{constraints} over variables $\boldsymbol{v}$ and $o$ is an 
\emph{objective function} $o : \boldsymbol{v} \mapsto \mathbb{R}$ to be 
(w.l.o.g.) minimized. 
A valuation such that all variables in $\boldsymbol{v}$ map 
to exactly one value, and all the constraints in $C$ are satisfied by the 
valuation is a \emph{solution} to $P$. A solution $\theta^*$ is optimal if$\not 
\exists \theta, \theta(\boldsymbol{v}) < \theta^*(\boldsymbol{v})$.

CP allows the user to model a COP and give it 
to a solver that will find solutions while optimizing 
the objective function (and prove optimality).

@@

\subsection{\relonto{} in Constraint Programming\label{SEC:rel2ontocp}}
We used the \minizinc{} language 
\cite{minizinc}, and the 
\chuffed{} solver. \cite{chu2011improving}\forijcai{ because it has a global constraint 
implemented for Steiner 
Tree Problems \cite{deuna2016steiner}. The model can be found in Appendix \ref{Ann:MZ}}

Because attributes must be connected to exactly one node of the alignment 
graph, and that node will be in $\mathcal{D_{G_O}} \cap V^\star$, 
then the part of the problem between attribute nodes and the alignment graph is 
actually a matching problem. Each attribute must match exactly one node of 
$\mathcal{D_{G_O}}$. Note that not all nodes in $\mathcal{D_{G_O}}$ need to match 
to an attribute, as not all of them are part of $T^\star$.

Since there are global constraints in CP specialized in matching 
\cite{regin1994filtering}, we split the problem into two parts: the 
$\mathit{steiner}$ global constraint \cite{deuna2016steiner} will only deal with the part of the 
integration graph that corresponds to the alignment graph, and the 
$\mathit{alldifferent}$ global constraint will deal with the matching part of 
the problem.

We use the following variables to represent the tree $T^\star$: Boolean 
variables $c_n,\forall n \in 
\mathcal{V_O}$, $c_e, \forall e \in	\mathcal{E_O}$ and an array of variables 
$match$ indexed by the set of attributes of $s^\star$. The combination of these 
sets of variables define the value of $T^\star$: $c_n = \mathit{true}$ means 
that $n \in V^\star$, $c_e = \mathit{true}$ means that $e \in E^\star$ and 
$match[a] = d$ (for $a \in \mathcal{A}_{s^\star}$ and $d \in 
\mathcal{D_{G_O}}$) means that the edge $(a,d) \in 
\mathcal{M}_\mathcal{O}^{s^\star}$ is part of $T^\star$.

@@

Eq.~\ref{EQ:obj} is the objective function: we are minimizing the cost 
of $T^\star$ while collecting prizes for each pattern we use. 
Eq.~\ref{EQ:stp} enforces that the solution 
$T^\star$ is indeed a tree defined by the $c_n$ and $c_e$ variables,
subgraph of the alignment graph 
and of total weight $w_{STP}$. 
Eq.~\ref{EQ:deg1} and \ref{EQ:deg2} ensure 
that if a data node of the alignment graph is selected, then at most one edge 
reaches it (from the side of the alignment graph) and otherwise it is 
disconnected. 
\ignore{Eq. \ref{EQ:matchdom} ensures that the domain of each 
variable in 
the array $match$ corresponds to a subset of data nodes of the alignment graph 
for which there is an edge connecting to the attribute at hand. 
Eq.~\ref{EQ:alld} ensure that each attribute is mapped to exactly one data node of 
the alignment graph.}
Eq.~\ref{EQ:matchdom} and \ref{EQ:alld} ensure that 
there is exactly one data node matched to an attribute. 
Eq.~\ref{EQ:map} ensures that 
if a data node of the alignment graph has been mapped to some attribute, then 
that data node must be in the solution tree, and vice-versa. 
Eq.~\ref{EQ:matchcost} computes the cost $w_{ADIFF}$ of the matches.
Eq.~\ref{EQ:patt} indicates that a pattern is used if and only if all its edges are selected in the tree. 
Eq.~\ref{EQ:pcost} computes the prizes collected by using patterns.
Eq. \ref{EQ:unk} ensures that if the \emph{unknown} class node is used, then it 
is connected to \emph{root}.
Notice there is no further requirement for unmatched attributes, as the 
$unk_i$ data nodes behave like normal data nodes, and the connectedness 
requirement will make sure that \emph{root} is connected to the rest of the 
tree (i.e. the semantic model).

@@

% datasets for evaluation
For the rest of the paper, we call our system \serene{} if no patterns are used in the model, and \serenepats{} otherwise.

We run experiments on two domains: museum (29 sources, 20 labels, 443 attributes and 159 \emph{unknown}s) and soccer (12 sources, 18 labels, 138 attributes and 45 \emph{unknown}s).% (see Fig.~\ref{tab:data} for statistics).

@@

\begin{figure}[t]\small
\centering
\begin{tikzpicture}[scale=0.35]
\pgfplotsset{
    scale only axis,
    xmin=0, xmax=9
}

>>>>

In our case, we would like this global model to account not only for structural properties of the original data sources, but also to include the semantics, which is usually implicitly present in the sources.
In other words, we want to build a semantic model which describes the data sources in terms of concepts and relationships defined by an ontology \cite{taheriyan2016learning}.
Henceforth, we focus on a specific data integration problem: automatically mapping a new relational data source onto a user provided ontology.
}
Relational data sources are still one of the most popular ways to store enterprise or Web data. However, the issue with relational schema is the lack of a well-defined semantic description.
A common ontology provides a way of representing the meaning of a relational schema and can facilitate the integration of heterogeneous data sources\forijcai{ within a domain}.
Indicating semantic correspondences manually might be appropriate if only few data sources need to be integrated, however, it becomes tedious with the growing number of heterogeneous schemata.

@@

%\subsubsection{Example} 
Consider the situation where we have some simple relational database tables with columns $\langle$\textit{Surname, Event, Date}$\rangle$, and 
$\langle$\textit{Company, Festival, Address}$\rangle$.
We do not \textit{a priori} know if ``Date'' is a 
date of birth of the person or the start date of the event (c.f. Fig. \ref{FIG:onto}); or whether 
``Address'' refers to the name of the place where the festival is located, or the 
email address of the company. 
Given an ontology like in Fig. \ref{FIG:onto}, we would like to automatically map new data sources to  the 
ontology.\forijcai{\hfill$\square$}

@@

Firstly, we build a graph which includes attributes (i.e. columns) from the new
source as well as ontology classes and properties.
We name it \emph{integration graph}.
It uses information gathered from previously mapped data sources, and is further extended with information derived from the ontology.
%Firstly, we build a \emph{integration graph} which includes the 
%attributes from the new source as well as ontology classes and properties.
Secondly, we apply ML techniques to 
assign costs to its edges. 
Lastly, we use CP to 
find a minimum cost Steiner Tree in the graph.
The goal is to assign the costs on the edges in such a way that the resulting 
Steiner Tree is a valid and coherent semantic model for the new source. 
Our contributions are:
%\begin{itemize}
	%\item 
	a novel modeling framework for the \relonto{} problem that uses ML, KRR and CP techniques;
%	\npr{symbolic AI, ontological reasoning, transitive closure}
	%\item
	an efficient approach to handle attributes which cannot be matched to 
	the ontology; \forijcai{through a new semantic labeling model and a new STP 
	model with additional nodes in the integration graph.}
	%\item 
	a flexible and extensible approach to the problem, easy to 
	reuse and adapt to specific situations through the use of CP.\forijcai{ allows introduction of additional constraints with no changes to the solver.} 
%\end{itemize}

@@

\begin{figure}[!t]
	\centering
	\scalebox{0.8}{
		\begin{tikzpicture}
		\begin{scope}
		\node[class] (pe) at (0,0)  {Person};
		\node[class] (co) at (0,-2) {Organisation};
		\node[class] (ev) at (3,0.2) {Event};
		\node[class] (pl) at (5,-1) {Place};
		\node[class] (ci) at (3,-2.5) {City};
		\node[class] (st) at (5,-2.5) {State};

@@

		\end{scope}
		\begin{scope}[xshift=7cm]
		\path[hasaC,->] (0,0)  to
		(0.5,0) ;
		\node[text=black,text width=2cm] (legend1) at (1.7,0)  
		{\small 
			``has an object property''};

		\path[hasaA,->] (0,-1.2)  to
		(0.5,-1.2) ;
		\node[text=black,text width=2cm] (legend1) at (1.7,-1.2)  
		{\small 
			``has a data property''};

		\path[isa,->] (0,-1.9)  to
		(0.5,-1.9) ;
		\node[text=black,text width=2cm] (legend1) at (1.7,-1.9)  
		{\small 
			``subClassOf''};

		\end{scope}
		\end{tikzpicture}
	}
	\caption{Example of ontology \forijcai{
			(`\protect\tikz{ \protect\node[class, inner sep = 2] () at (0,0)  {};}' are Classes, `\protect\tikz{ \protect\path[hasaC,->] 
				(0,1) -- (3ex,1);}' means ``has an object property'', 
			`\protect\tikz{ \protect\path[hasaA,decoration={post length=0}] (0,0) edge[decorate] (3ex,0);}' 
			means ``has a data property'' and 
			`\protect\tikz{ \protect\path[isa,->] (0,1) -- (3ex,1);}' means ``subClassOf'' ). Example }by
		\protect\citeasnoun{Taheriyan2013}.
	}
	\label{FIG:onto}
	\vspace{-3mm}
\end{figure}

A \emph{semantic model} $m$ is a directed graph with two types of nodes: 
\emph{class nodes} and \emph{data nodes}. 
We denote them as $\mathcal{C}_m$ and $\mathcal{D}_m$, respectively.
$ \mathcal{C}_m$ corresponds to classes in the ontology 
whereas $\mathcal{D}_m$ corresponds to data 
properties. 
Edges in the semantic model correspond to properties in the ontology, as 
shown in Fig.~\ref{FIG:sem} (notice the same edges appear in Fig.~\ref{FIG:onto}).
The semantic model may have several instances of the same ontology class, that is why class nodes are enumerated.
\forijcai{Semantic models can be formalized using a standard mapping language such as R2RML~\cite{r2rml}.}

@@

\subsection{Semantic Labeling}
The semantic types $\mathcal{L_O} = \{l_1, l_2, ..., l_p\}$ of an ontology 
correspond to all pairs $(c,d)$, where $c$ is a Class in $\mathcal{O}$, and $d$ 
is a data property of that class (including inherited properties). 
E.g., in Fig. \ref{FIG:onto}, we would get
(City,name) and (State,name).

The first step to model the semantics of a new source $s^\star$ is to recognize the semantic types present in the source. 
We call this step \emph{semantic labeling}, which assigns a confidence value to a match of an attribute from $s^\star$ to a type $l \in 
\mathcal{L_O}$.
Typically semantic labeling techniques encounter several problems such as:
naming conflicts~\cite{Pinkel:rodi}, multiple data representations, and semantically different attributes might have syntactically similar 
content. %, for example, startDate versus endDate for the Event class.
Also, there may be a considerable number of attributes which have no 
corresponding property in the ontology (accidentaly or deliberately).
%\ddg{CHECK!}

We formulate the problem of semantic labeling as a multi-class classification
problem.
The known source descriptions $\Delta_T$ provide us the training sample.
We compute a feature vector for each attribute in a data source and associate 
the known semantic type with the corresponding feature vector.
The feature vector includes, among others, characteristics
such as a number 
of whitespaces and other special characters, statistics of 
values in the column. 
\forijcai{A full list can be found in Appendix \ref{Ann:SemLab}.}
%\npr{If I remove entropy descr, we are perfectly within page limit}
%\ignore{
One of the important features characterising information content of an attribute is Shannon's entropy.
% of the attribute's concatenated rows
Shannon's entropy 
%(or information entropy~\cite{Manning:Introduction})
 of a string $X$ is defined as
$H(X) = -\sum_{i}{p_i \log_{2}p_i},$ where $p_i$ is the probability of a character, whose index in character vocabulary is $i$, to appear in $X$, and the summation ranges over all
characters in the vocabulary.
%of all possible characters
To evaluate $p_i$ in Shannon's entropy, we evaluate normalized character frequency distribution \emph{chardist} of an attribute, as character counts in concatenated rows of the attribute, normalized by the total length of the concatenated rows.
The alphabet\forijcai{vocabulary of all characters} consists of 100 printable characters\forijcai{ (including $\backslash$n)}.
Finally, we add the 100-dimensional vector of $p_i$ to the attribute feature vector.
%}
We also compute a set of features based on similarity metrics inspired by state-of-the-art works by ~\citeasnoun{Pham:semantic} or~\citeasnoun{Ritze:matching}.
Among others, we compute mean cosine similarity for character distributions of attribute values and string similarity metrics for attribute names.
%To extract features from attribute names, we compute string similarity metrics: minimum edit distance, two WordNet based similarity measures such as JCN~\cite{Jiang:Semantic} and LIN ~\cite{Lin:Information}, and $k$-nearest neighbors using Needle-Wunsch distance~\cite{Needleman:General}.
%The minimum edit distance between two strings $s_1$ and $s_2$ is the minimum number of edit operations, such as insertion, deletion, substitution, which are required to transform one string into another~\cite{Manning:Introduction}.
%We compute the similarity between attribute name and all class instances in the training data.
%The number of thus extracted features depends on the number of semantic labels in the training data.
We train a random forest on the obtained sample.

@@

To provide an integrated view over the known source descriptions $\Delta_T$, we 
align their semantic models as well as all semantic 
types. 
This is done by building an \emph{alignment graph}.

@@

The graph is weighted by a function $w_\mathcal{O} : \mathcal{E_O} \mapsto 
\mathbb{R}$ such that edges which are present in
the known semantic models have lower weights than those 
which are inferred from the ontology.
\forijcai{In the next section we will see that this makes edges from semantic models 
more attractive. }
\citeasnoun{taheriyan2016learning} provide details on the weighting function.
%\ddg{How exactly are they weighted?}
An example alignment graph is illustrated in Fig.~\ref{FIG:ali}. 
%Bigger examples can be found in \cite{Taheriyan2013}. 
\forijcai{Black links are links supported by the known semantic models. 
Blue links are inferred from the ontology.(the orange 
ones correspond to the ones added to connect Classes of the ontology that never 
appeared in the semantic models).}
% and can be assigned the 
%maximum weight $w_max$ \ddg{where does this weight come from?}

\begin{figure}[ht]
\centering \scalebox{0.8}{
\begin{tikzpicture}[scale=0.9]
\begin{scope}[xshift=-10]

@@

\end{scope}
\begin{scope}[xshift=7cm]
	\path[hasaC,->] (0,0)  to
	 (0.5,0) ;
	 \node[text=black,text width=2cm] (legend1) at (1.7,0)  
	 {\small 
	 	Link supported by known semantic models};

	 	\path[isa,->,blue!70] (0,-1.2)  to
	 	(0.5,-1.2) ;
	 		 	\path[hasaC,->,blue!70] (0,-1.5)  to
	 		 	(0.5,-1.5) ;
	 	\node[text=black,text width=2cm] (legend1) at (1.7,-1.3)  
	 	{\small 
	 		Links inferred from ontology};
\end{scope}
\end{tikzpicture}}
\caption{Example of alignment graph (`\protect\tikz{ \protect\node[class, inner sep = 2] () at (0,0)  
{};}' \forijcai{`\protect\tikz{ \protect\node[class,orange,fill=orange!30!white,text=black, inner sep = 2] () at 
(0,0)  
{};}'} are class nodes, and `\protect\tikz{ \protect\node[data] () at (0,0)  {};}' are data 
nodes). We omit weights for clarity.}
\label{FIG:ali}
\vspace{-3mm}
\end{figure}

@@

Given a graph $G =
(V, E)$ and a subset of its nodes $T \subseteq V$, a 
Steiner Tree $G_s = (V_s, E_s )$ is a tree \forijcai{(connected acyclic graph) }such that 
$T \subseteq V_s \subseteq 
V$ and $E_s \subseteq E$. 
That is\forijcai{In other words}, $G_s$ spans all the nodes in $T$ and 
may include additional nodes from $V$\forijcai{, in particular} to ensure the 
connectedness of the constructed tree. 
The Steiner Tree Problem 
(STP) is stated as follows: given $G$ and a weight function $w_f : E 
\mapsto \mathbb{R}$, find the Steiner Tree that minimizes the sum of the 
weights of the edges in $E_s$\forijcai{ given by $w_f$}. This was proven to be NP-hard 
by \citeasnoun{Karp1972}.

@@

\begin{figure}[ht]
\centering \scalebox{0.8}{
\begin{tikzpicture}[scale=0.9]
\begin{scope}
	\node[class, rectangle, rounded corners] (CLASS) at (0,0) { \small{ 
	Class nodes of Alignment Graph (i.e. $\mathcal{C_{G_O}}$)}};

@@

	\path[draw] (a4) -- (stn1);
	\path[draw] (a4) -- (cin1);
	\path[draw] (a4) -- (con1);
	\path[draw] (a4) -- (cin2);
	\path[draw] (a4) -- (con2);
	\end{scope}
	\begin{scope}[xshift=5cm]
\node[att] () at (0,0)  
{};  
\node[text=black,text width=1.5cm] (legend1) at (1.3,0)  
{\small 
	Attribute nodes};

	\end{scope}
\end{tikzpicture} }
\caption{Example of integration graph. We omit weights and only show the most likely 
matches for clarity.\forijcai{ Data node
are the same as in Fig. \ref{FIG:ali}.}}
\label{FIG:inte}
\vspace{-3mm}
\end{figure}

@@

\textbf{Patterns:}
As explained in Sec. \ref{SSEC:pattern-mining}, we use 
graph patterns to incentivise the solution tree 
$T^\star$ to contain subgraphs of the alignment graph that have been frequently 
seen in the training set.
To do this, we use the support of each obtained patterns as a prize. If 
the tree contains a pattern, then its weight is automatically reduced by the 
value of the support of that pattern. \forijcai{Sec. \ref{SEC:rel2ontocp} shows how this is integrated in the model.}

@@

If an attribute $a$ is matched to $unk_a$, then $unk_a$ will be linked to Class 
node \emph{unknown}. 
The other attributes can be matched normally 
and build a semantic model as usual. 
To maintain connectedness of $T^\star$, the \emph{unknown} node and one of the other Class nodes in $T^\star$ 
will 
both be connected to the \emph{root} node. 
Note that if all attributes find a 
match, then neither \emph{unknown} or \emph{root} will be selected and the normal behavior will take place.
The weights of the edges between these special nodes are
assigned the same way as for the rest of the edges.
%\ddg{Explain the weights of the edges introduced by the unknown nodes}

@@

A Constraint Optimization Problem (COP) is a tuple $P=(\boldsymbol{v},C,o)$ 
where $\boldsymbol{v}$ is a 
set of \emph{variables}, $C$ is a set of $n$-ary 
\emph{constraints} over variables $\boldsymbol{v}$ and $o$ is an 
\emph{objective function} $o : \boldsymbol{v} \mapsto \mathbb{R}$ to be 
(w.l.o.g.) minimized. 
A valuation such that all variables in $\boldsymbol{v}$ map 
to exactly one value, and all the constraints in $C$ are satisfied by the 
valuation is a \emph{solution} to $P$. A solution $\theta^*$ is optimal if$\not 
\exists \theta, \theta(\boldsymbol{v}) < \theta^*(\boldsymbol{v})$.
CP allows the user to model a COP and give it 
to a ``black-box'' solver to find solutions while optimizing 
the objective function\forijcai{ (and prove optimality)}.

@@

\subsection{\relonto{} in Constraint Programming\label{SEC:rel2ontocp}}
We used the \minizinc{} language 
\cite{minizinc}, and the 
\chuffed{} solver \cite{chu2011improving}. \forijcai{ because it has a global constraint 
implemented for Steiner 
Tree Problems \cite{deuna2016steiner}. The model can be found in Appendix \ref{Ann:MZ}}

Since attributes must be connected to exactly one node of the alignment 
graph, and that node will be in $\mathcal{D_{G_O}} \cap V^\star$, 
then the part of the problem between attribute nodes and the alignment graph is 
\forijcai{actually} a matching problem. Each attribute must match exactly one node of 
$\mathcal{D_{G_O}}$. Note that not all nodes in $\mathcal{D_{G_O}}$ need to match 
to an attribute, as they are not all part of $T^\star$.

Because there are global constraints in CP specialized in matching 
\cite{regin1994filtering}, we split the problem into two parts: the 
$\mathit{steiner}$ global constraint \cite{deuna2016steiner} will only deal with the part of the 
integration graph that corresponds to the alignment graph, and the 
$\mathit{alldifferent}$ global constraint will deal with the matching part of 
the problem.

We use Boolean 
variables $c_n,\forall n \in 
\mathcal{V_O}$, $c_e, \forall e \in	\mathcal{E_O}$ and an array of variables 
$match$ indexed by the set of attributes of $s^\star$ to represent the tree $T^\star$: $c_n = \mathit{true}$ means 
that $n \in V^\star$, $c_e = \mathit{true}$ means that $e \in E^\star$ and 
$match[a] = d$ (for $a \in \mathcal{A}_{s^\star}$ and $d \in 
\mathcal{D_{G_O}}$) means that the edge $(a,d) \in 
\mathcal{M}_\mathcal{O}^{s^\star}$ is part of $T^\star$.

@@

Eq.~\ref{EQ:obj} is the objective function: we minimize the cost 
of $T^\star$ while collecting prizes for each pattern we use. 
Eq.~\ref{EQ:stp} enforces the solution 
$T^\star$ to be a tree defined by the $c_n$ and $c_e$ variables,
subgraph of $\mathcal{G_O}$%the alignment graph 
and of total weight $w_{STP}$. 
Eqs.~\ref{EQ:deg1} and \ref{EQ:deg2} ensure 
that if a data node of $\mathcal{G_O}$ is selected, then at most one edge 
reaches it (from the side of $\mathcal{G_O}$) and otherwise it is 
disconnected. 
\ignore{Eq. \ref{EQ:matchdom} ensures that the domain of each 
variable in 
the array $match$ corresponds to a subset of data nodes of $\mathcal{G_O}$ 
for which there is an edge connecting to the attribute at hand. 
Eq.~\ref{EQ:alld} ensure that each attribute is mapped to exactly one data node of 
$\mathcal{G_O}$.}
Eqs.~\ref{EQ:matchdom} and \ref{EQ:alld} ensure that 
there is exactly one data node matched to an attribute. 
Eq.~\ref{EQ:map} ensures that 
if a data node of $\mathcal{G_O}$ has been mapped to some attribute, then 
that data node must be in the solution tree, and vice-versa. 
Eq.~\ref{EQ:matchcost} computes the cost $w_{ADIFF}$ of the matches.
Eq.~\ref{EQ:patt} indicates that a pattern is used if and only if all its edges are selected in the tree. 
Eq.~\ref{EQ:pcost} computes the prizes collected by using patterns.
Eq. \ref{EQ:unk} ensures that if the \emph{unknown} class node is used, then it 
is connected to \emph{root}.
Notice there is no further requirement for unmatched attributes, as the 
$unk_i$ nodes behave like normal data nodes, and the connectedness 
requirement will make sure that \emph{root} is connected to the rest of the 
tree (i.e. the semantic model).

@@

% datasets for evaluation
From now on, we call our system \serene{} if no patterns are used in the model, and \serenepats{} otherwise.
We run experiments on two domains: museum (29 sources, 20 labels, 443 semantic attributes and 159 \emph{unknown} attributes) and soccer (12 sources, 18 labels, 138 attributes and 45 \emph{unknown}s).% (see Fig.~\ref{tab:data} for statistics).

@@

\begin{figure}[t]\small
\centering
\begin{tikzpicture}[scale=0.3]
\pgfplotsset{
    scale only axis,
    xmin=0, xmax=9
}
